Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-03-18 article/figures.Rmd
+ @Zongle comments incorperated to article + final dataset added to ms
+ fix bug

# set options
options(error=NULL)
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.cap='The effectiveness of prioritizations at securing genetic variation. The top row of panels (a--b) show the performance of single-species prioritizations generated assuming equal costs among planning costs. The middle row of panels (c--d) show the performance of multi-species prioritizations generated assuming equal costs among planning units. The bottom row of panels (e--f) show the performance of multi-species prioritizations generated using opportunity costs. The left column of panels (a, c, d) and the right column of panels (b, d, f) show the proportion of adaptive and neutral genetic variation secured (respectively). Box plots show the effectiveness of prioritizations generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Letters denote significant differences ($P < 0.05$).'}
# prepare data for plotting
results.SDF <- results.SDF %>% mutate(
		Prioritisation=factor(as.character(Prioritisation), levels=c('Amount','Surrogate','Genetic')),
		Context=factor(as.character(Context), levels=c("single-species (equal costs)", "multi-species (equal costs)", "multi-species (opportunity costs)")),
		Metric=factor(as.character(Metric), c("Adaptive variation", "Neutral variation"))
	)
results.PDF <- results.SDF %>% group_by(
		Prioritisation, Context, Metric
	) %>% mutate(
		letter.height=max(value, na.rm=TRUE)+0.1,
		Combination=paste0(Prioritisation,'.',Metric,'.',Context)
	) %>% filter(
		c(TRUE, rep(FALSE, length(Context)-1))
	) %>% data.frame() %>% group_by(Context, Metric) %>% mutate(
		panel.letter=paste0('(',letters[as.integer(Context) + (as.integer(Metric)-1)],')'),
		panel.letter=c(as.character(panel.letter[1]), rep(NA_character_, length(Context)-1))
	) %>% data.frame() %>% left_join(
		data.frame(
			letter=unname(toupper(cld(posthoc.model.GLHT)$mcletters$Letters)),
			Combination=as.character(names(toupper(cld(posthoc.model.GLHT)$mcletters$Letters)))
		) %>% mutate(Combination=as.character(Combination)),
		by='Combination'
	) %>% data.frame()
results.SDF <- results.SDF %>% mutate(
	Context=sapply(as.character(Context), function(x) {paste0(toupper(substr(x, 1, 1)), substr(x, 2, nchar(x)))}),
	Context=factor(
		gsub(' (', '\n(', Context, fixed=TRUE),
		levels=c("Single-species\n(equal costs)",
		"Multi-species\n(equal costs)", 
		"Multi-species\n(opportunity costs)"))
	)
results.PDF <- results.PDF %>% mutate(
	Context=sapply(as.character(Context), function(x) {paste0(toupper(substr(x, 1, 1)), substr(x, 2, nchar(x)))}),
	Context=factor(
		gsub(' (', '\n(', Context, fixed=TRUE),
		levels=c("Single-species\n(equal costs)",
		"Multi-species\n(equal costs)", 
		"Multi-species\n(opportunity costs)"))
	)

>>>>

# set options
options(error=NULL)

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.cap='The effectiveness of prioritizations at securing genetic variation. The top row of panels (a--b) show the performance of single-species prioritizations generated assuming equal costs among planning costs. The middle row of panels (c--d) show the performance of multi-species prioritizations generated assuming equal costs among planning units. The bottom row of panels (e--f) show the performance of multi-species prioritizations generated using opportunity costs. The left column of panels (a, c, d) and the right column of panels (b, d, f) show the proportion of adaptive and neutral genetic variation secured (respectively). Box plots show the effectiveness of prioritizations generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Letters denote significant differences ($P < 0.05$).'}
# prepare data for plotting
results.SDF <- results.SDF %>% mutate(
		Prioritisation=factor(as.character(Prioritisation), levels=c('Amount','Surrogate','Genetic')),
		Context=factor(as.character(Context), levels=c("single-species (equal costs)", "multi-species (equal costs)", "multi-species (opportunity costs)")),
		Metric=factor(as.character(Metric), c("Adaptive variation", "Neutral variation"))
	)
results.PDF <- results.SDF %>% group_by(
		Prioritisation, Context, Metric
	) %>% mutate(
		letter.height=max(value, na.rm=TRUE)+0.1,
		Combination=paste0(Prioritisation,'.',Metric,'.',Context)
	) %>% filter(
		c(TRUE, rep(FALSE, length(Context)-1))
	) %>% data.frame() %>% group_by(Context, Metric) %>% mutate(
		panel.letter=paste0('(',letters[as.integer(Context) + (as.integer(Metric)-1)],')'),
		panel.letter=c(as.character(panel.letter[1]), rep(NA_character_, length(Context)-1))
	) %>% data.frame() %>% left_join(
		data.frame(
			letter=unname(toupper(cld(posthoc.scenario.GLHT)$mcletters$Letters)),
			Combination=as.character(names(toupper(cld(posthoc.scenario.GLHT)$mcletters$Letters)))
		) %>% mutate(Combination=as.character(Combination)),
		by='Combination'
	) %>% data.frame()
results.SDF <- results.SDF %>% mutate(
	Context=sapply(as.character(Context), function(x) {paste0(toupper(substr(x, 1, 1)), substr(x, 2, nchar(x)))}),
	Context=factor(
		gsub(' (', '\n(', Context, fixed=TRUE),
		levels=c("Single-species\n(equal costs)",
		"Multi-species\n(equal costs)", 
		"Multi-species\n(opportunity costs)"))
	)
results.PDF <- results.PDF %>% mutate(
	Context=sapply(as.character(Context), function(x) {paste0(toupper(substr(x, 1, 1)), substr(x, 2, nchar(x)))}),
	Context=factor(
		gsub(' (', '\n(', Context, fixed=TRUE),
		levels=c("Single-species\n(equal costs)",
		"Multi-species\n(equal costs)", 
		"Multi-species\n(opportunity costs)"))
	)
